Output Summary

### 2022-04-12 03-post-process/output-plots.Rmd
Fix duplication/subsetting issues with MCMC diagnostic summary table

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Overwinter survival: Fall Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Spring Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# LGR to Ocean Migration survival: NOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: HOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Probability of Maturing at Age-3: NOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-3: HOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: NOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: HOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# BON to LGR Migration survival: NOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: HOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Pre-spawn Survival
L1 = "Pre-spawn Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # predict parr recruits along a sequence of spawner abundances
  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  E_pred = seq(0, max(E[5,]), length = 30)

>>>>

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Overwinter survival: Fall Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Spring Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# LGR to Ocean Migration survival: NOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: HOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Probability of Maturing at Age-3: NOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-3: HOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: NOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: HOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# BON to LGR Migration survival: NOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: HOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Pre-spawn Survival
L1 = "Pre-spawn Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

  # extract posterior summaries of total spawners by brood year
  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # predict parr recruits along a sequence of spawner abundances
  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  E_pred = seq(0, max(E[5,]), length = 30)
